Data processing

### 2024-05-22 scripts/data_processing.qmd
adding a chunk to get the number of observations and trials
adding the country variable to the dataset

        data_plot_level %>%
            filter (pmid %in% pmids$pmid) %>%
            select (pmid, tan.app, app.method, app.rate, man.dm, man.ph, man.source, incorp, time.incorp) %>%
            rename (app.mthd = app.method, t.incorp = time.incorp),

@@

@@

```{r}
# data = data_ml
# pmids = data %>% pull (pmid) %>% unique
# 
# data_ml = NULL
# 
# for (i in pmids) {
#         
#     data_tmp = data %>% filter (pmid == i)
#     
#     time_max = max (data_tmp$time)
#     
#     time = seq (0, (time_max - 0.01), by = 0.01)
#     
#     group = c(
#         sapply (c (1 : 5), function (j) rep (j, 400)) %>% as.vector,
#         rep (6, (length (time) - 2000))
#     )
#     
#     # here we added 1+e-8 for numerical reasons, ('19.8 - 16.7 <= 3.1' return FALSE)
#     temp = sapply (time, function (j) data_tmp %>% filter ((time - dt) <= j + 1e-8 & j + 1e-8 < time) %>% pull (air.temp))
#     wind = sapply (time, function (j) data_tmp %>% filter ((time - dt) <= j + 1e-8 & j + 1e-8 < time) %>% pull (wind.2m))
#     rain = sapply (time, function (j) data_tmp %>% filter ((time - dt) <= j + 1e-8 & j + 1e-8 < time) %>% pull (rain.rate))
# 
# 
#     df_temp = data.frame (time = time, temp = temp, group = group) %>% 
# 
#         summarise (temp = mean (temp), .by = group) %>% 
#         pivot_wider (names_from = group, values_from = temp, names_prefix = "temp_")
#                    
# 
#     df_wind = data.frame (time = time, wind = wind, group = group) %>% 
# 
#         summarise (wind = mean (wind), .by = group) %>% 
#         pivot_wider (names_from = group, values_from = wind, names_prefix = "wind_")
#                    
# 
#     df_rain = data.frame (time = time, rain = rain, group = group) %>% 
# 
#         summarise (rain = mean (rain), .by = group) %>% 
#         pivot_wider (names_from = group, values_from = rain, names_prefix = "rain_")
# 
# 
#     data_tmp = cbind (
#         data_tmp[nrow (data_tmp), ] %>% select (dataset, e.cum, e.rel, pmid, time, tan.app, app.mthd, app.rate, man.dm, man.ph, man.source, incorp, t.incorp),
#         df_temp,
#         df_wind,
#         df_rain
#     )
#                    
#     data_ml = rbind (data_ml, data_tmp)
#                                                          
# }

# save (processed_data/data_ml, file = "data_ml.Rdata")

@@

>>>>

        data_plot_level %>%
            filter (pmid %in% pmids$pmid) %>%
            select (pmid, country, tan.app, app.method, app.rate, man.dm, man.ph, man.source, incorp, time.incorp) %>%
            rename (app.mthd = app.method, t.incorp = time.incorp),

@@

```{r}
df_join = data_alfam2 %>% select (pmid, country) %>% distinct
```

```{r}
data_alfam2 %>%
  summarise (n_obs = n(), n_trial = length (unique (pmid)))
```

@@

```{r}
# data = data_ml
# pmids = data %>% pull (pmid) %>% unique
# 
# data_ml = NULL
# 
# for (i in pmids) {
#         
#     data_tmp = data %>% filter (pmid == i)
#     
#     time_max = max (data_tmp$time)
#     
#     time = seq (0, (time_max - 0.01), by = 0.01)
#     
#     group = c(
#         sapply (c (1 : 5), function (j) rep (j, 400)) %>% as.vector,
#         rep (6, (length (time) - 2000))
#     )
#     
#     # here we added 1+e-8 for numerical reasons, ('19.8 - 16.7 <= 3.1' return FALSE)
#     temp = sapply (time, function (j) data_tmp %>% filter ((time - dt) <= j + 1e-8 & j + 1e-8 < time) %>% pull (air.temp))
#     wind = sapply (time, function (j) data_tmp %>% filter ((time - dt) <= j + 1e-8 & j + 1e-8 < time) %>% pull (wind.2m))
#     rain = sapply (time, function (j) data_tmp %>% filter ((time - dt) <= j + 1e-8 & j + 1e-8 < time) %>% pull (rain.rate))
# 
# 
#     df_temp = data.frame (time = time, temp = temp, group = group) %>% 
# 
#         summarise (temp = mean (temp), .by = group) %>% 
#         pivot_wider (names_from = group, values_from = temp, names_prefix = "temp_")
#                    
# 
#     df_wind = data.frame (time = time, wind = wind, group = group) %>% 
# 
#         summarise (wind = mean (wind), .by = group) %>% 
#         pivot_wider (names_from = group, values_from = wind, names_prefix = "wind_")
#                    
# 
#     df_rain = data.frame (time = time, rain = rain, group = group) %>% 
# 
#         summarise (rain = mean (rain), .by = group) %>% 
#         pivot_wider (names_from = group, values_from = rain, names_prefix = "rain_")
# 
# 
#     data_tmp = cbind (
#         data_tmp[nrow (data_tmp), ] %>% select (dataset, e.cum, e.rel, pmid, country, time, tan.app, app.mthd, app.rate, man.dm, man.ph, man.source, incorp, t.incorp),
#         df_temp,
#         df_wind,
#         df_rain
#     )
#                    
#     data_ml = rbind (data_ml, data_tmp)
#                                                          
# }

# save (data_ml, file = "processed_data/data_ml.Rdata")

@@

```{r}
dim (data_ml)
```
